Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-25 paper/ms.tex
update ms
(add B-star connection)

The most massive CQVs in our sample might represent an interesting new
regime.  To date, the only stars reported to show the CQV phenomenon
are M-dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
\citep{2022AJ....163..144G}.  TIC~405754448 and TIC~405910546 however
appear to have masses of $\approx$0.82 and $\approx$0.60\,$M_\odot$
respectively.  The next-highest masses are $\approx$0.40\,$M_\odot$.
The masses for the former two objects are consistent with their CAMD
locations, and their membership in LCC.  Based on its light curve
morphology, TIC~405910546 should be studied in greater depth, to
confirm it is not an eclipsing binary.  TIC~405754448 similarly shows
distinct morphology from many of the CQVs in Figure~\ref{fig:cqvs}, in
that it has some of the lowest amplitude dips.  While TIC~405754448
might be an unresolved binary (RUWE$_{\rm DR3}$=4.7),  the lack of
secondary peaks in its periodogram and the coherent dips present in
the Sector~11 light curve suggest that the CQV signal is indeed from
the apparent primary of the system.  Taken in sum, both of these
objects seem to suggest that the CQV phenomenon extends up in mass to
pre-main-sequence K-dwarfs.

@@

Any link between the dense gas clumps (prominences) that likely exist
around rapidly rotating low-mass stars and the CQV phenomenon has
yet to be made.  A simple visual examination of the TESS light curves
for five prominence-hosting systems studied by
\citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and
V374 Peg--revealed no obvious CQV behavior, though all show
differential evolution, and Speedy~Mic shows two closely-spaced periods
and a strong beat.  Spectroscopically observable prominences 
do not imply CQV-like dips.

@@

\subsubsection{Can gas absorption reproduce the observed chromaticity?}
The strongest argument for why neutral hydrogen is an unlikely
occulting source is that CQVs show broadband flux variations that are
deeper in the blue than in the red.

Based on our reading of \citet[][Ch.~8]{1992oasp.book.....G}, it seems
challenging to get neutral hydrogen to have this type of
chromaticity.  Bound-bound absorption provides opacity only at narrow
resonant lines.  Bound-free absorption can provide
wavelength-dependent opacity, but the absorption coefficients
generally {\it grow} with increasing wavelength, rather than {\it
shrink} as one needs in order to get deeper absorption in the blue
than in the red.  H$^-$  fails as a viable opacity source for the same
reason: its absorption coefficient peaks near 8500\,\AA, and is an
order of magnitude smaller at $\approx$3000\AA.
(\citealt{1992oasp.book.....G}, following \citealt{1979MNRAS.187P..59W}).
Thompson scattering is also ruled out, because it is gray.  Dust, with
its larger absorption cross-section in the blue than the red
\citep{1989ApJ...345..245C}, is to our knowledge the most obvious
opacity source.

While the reasoning above seems fairly convincing, it has a
flaw.  The argument presented above would imply that regardless of a
star's temperature, if relative depths of a dip are seen to be deeper
in the blue than in the red, then it is hard to get hydrogen to do it.
There is however a rapidly rotating magnetic B-star, $\sigma$~Ori~E,
which shows dips that are deeper in the blue than in the red
\citep{1977ApJ...216L..31H}.  Photometric and spectroscopic
observations of this star have been understood in terms of absorbing
circumstellar material, analogous to the geometries we are
discussing for much cooler M-dwarfs \citep{2005ApJ...630L..81T}.  This
material however is unlikely to be dust, due to the relevant sublimation
timescales.  The opacity is instead thought to be sourced from bound-free
absorption from neutral hydrogen \citep{2005ApJ...630L..81T}.
Separate and smaller amplitude emission in that system may also come
from electrons scattering photospheric light toward the observer when
the clouds are not in transit \citep{2022MNRAS.511.4815B}.

Given these complexities, it clearly seems important for a future
theoretical study to be conducted to determine to what degree the
observed chromaticities in CQVs match, or do not match, expectations
from radiative transfer.  This issue has a key ability to resolve the
question of whether the CQVs are caused by dust, or by gas.  This
question has direct bearing on the potential utility of these objects.

@@

\subsubsection{The lifetime constraint}
Independent of the microphysical basis for gas absorption, the observed
lifetime of the CQV phenomenon could provide another dimension to discern between
the gas {\it vs.} dust clump scenarios.
Based on the available statistics from the studies by L.~Rebull and J.~Stauffer,
it seems plausible that CQV occurrence decreases in time, bottoming to zero
well before the $\approx$700\,Myr age of Praesepe.
This is odd in the context of the prominence scenario, because pre-main-sequence
M-dwarfs spin up over the first $\approx$$10^8$\,yr;
prominences might even be expected to be {\it more} common at the 
age of the Pleiades than for younger stars.
This broadly assumes that any star that can support prominences will,
which translates in detail to a condition on the star's mass, rotation
period, and magnetic field strength.
Based on the degree to which M-dwarfs remain rapid rotators over the first 700\,Myr
\citep[e.g. Figure~13 of][]{2022AJ....164...80R}, 
it seems surprising in the gas clump (prominence) scenario that no stars
older than 150\,Myr have been seen to exhibit the phenomenon.
In the dust clump scenario this is not a problem, because if the dust
were externally sourced, it would be expected to have a finite supply.

@@

Planet occurrence rate studies based on Kepler showed that around
(early) M-dwarfs, there are $\approx$0.1 planets per star with sizes
between 1-4\,$R_\oplus$ and orbital periods within 3 days
\citep{2015ApJ...807...45D}.  The number increases to $\approx$0.7
planets per star, for planets with 1-4\,$R_\oplus$ and $P$$<$10\,days.
Extrapolating to all small close-in planets, with say
0.1-4\,$R_\oplus$ and within 10 days, it is reasonable to expect on
average one planet per M-dwarf.  TRAPPIST-1b ($P$=1.5\,days) is one
example of this type of planet, in orbit around a 0.08\,$M_\odot$ star
\citep{2017Natur.542..456G}.

In the context of planet formation theory, the locations of these
close-in planets are set by the location of the protoplanetary disk's
magnetospheric truncation radius (see e.g. CITE for a review).  In
simple 1-D viscous accretion models, this truncation radius roughly
coincides with the corotation radius (CITE), though in detail factors
of a few difference have been observed between the two (CITE IR
studies).  Within models that have migrating compact multiplanet
resonant chains, the inner-most planets arrive within $\approx$5-10
stellar radii within the first 100\,Myr \citep{2018haex.bookE.142I}.

Given this context, it is tempting to try to interpret features of the
CQV light curves in terms of the possible presence of close-in
exoplanets, or even planetesimals.  Rocky planets this young would
likely have molten global magma oceans analogous to those that existed
on the Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus
would be undergoing significant outgassing and atmospheric escape.
However while a scenario in which close-in rocky planets or
planetesimals serve as a possible source of dust for the clouds is
{\it a priori} plausible, any evidence in support of such a picture
currently seems ambiguous at best.

@@

The planetesimal swarm model would also predict that certain orbital
phases would produce recurrent dips if observed over sufficiently long
timescales, since the launching planetesimal would be massive enough
to remain in orbit, and similar to say K2-22 would stochastically
eject material.  While the regularity of the dip phases of LP~12-502
over the existing baseline (Figure~\ref{fig:lp2}) might agree with
this prediction, 
for most other CQVs (Figure~\ref{fig:evoln}) the data seem likely to
be in tension with this expectation.

There are a few additional problems for the idea of a disintegrating
planetesimal swarm.  First, many of the dips show asymmetries in
the wrong direction relative to the naive expectation of a
trailing comet tail.  Invoking non-exponentially decaying dust
distributions as a function of azimuth might be one way out of this,
but such an idea would need stronger theoretical footing.  
Dynamical stability would be a separate concern:
in a model in which any new dip is ``explained'' by invoking a new
planetesimal, one might eventually pack the corotation radius to a
degree where instability over short timescales would be guranteed.

@@

It is amusing that in identifying the two ambiguous CQVs in
Section~\ref{subsec:irexcess} with outlying SEDs (TICs~193136669 and
TIC~57830249), we were prompted to reconsider our light curve-based
labeling, to
ultimately conclude that these sources are dippers.  This episode
suggests that there could be overlap between CQVs and dippers.  It is also worth emphasizing that our labeling of
e.g.~TIC~57830249 was based on a single sector of TESS data
(Sector~36) when its behavior is relatively periodic and it showed
dip depths of a few percent.  However in other TESS sectors
(e.g. Sector~10), this source looks completely different, varying in
apparent flux by a factor of two, with hardly any discernible
periodicity at all.

@@

@@

We can estimate the mass of a transiting cloud by first converting the
transit depth to an effective cloud radius, $R_{\rm cloud}$.  For most
CQVs in Figure~\ref{fig:cqvs}, this typically yields $\approx$2-20\,$R_\oplus$.
This size can be converted into a mass estimate by requiring the
optical depth $\tau$ of the cloud to be at least unity and by positing
some composition for the cloud.  In other
words, a minimum constraint on the number density follows by
requiring the cloud to be optically thick.  For cases like LP 12-502,
this is reasonable because the transit duration implies $R_{\rm
cloud}\ll R_\star$.  Carrying out the relevant calculation assuming
the occulting material is dust grains 1\,$\mu$m in size,
\citet{2023MNRAS.518.4734S} find minimum cloud masses of order
$10^{12}$\,kg (their Eq.~23), which scale linearly with both the
optical depth and dust grain radius.  This is comparable to a
small asteroid; the asteroid belt itself has a mass of
order $\approx$10$^{21}$\,kg (CITE).  
The previously discussed cool gas prominences would need to have
masses of order $10^{14}$\,kg \citep{1990MNRAS.247..415C}, about
100$\times$ larger than the requisite dust mass.

@@

\subsection{Is it inflow or outflow?}

The B-star analogy is an outflow.
Debris disks are an inflow.
It seems to match the B-star analogy.

@@

\begin{enumerate}[leftmargin=*]
	%
  \item CQVs are quasiperiodic.  The mean periods 
    remain fixed over the $>$1{,}000-cycle baseline of available
    observations; but the light curve shapes always evolve (Figure~\ref{fig:evoln}).
  %
  \item The same CQV can show dips with similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of its fundamental period,
    sometimes simultaneously, and each lasting for up to 50 cycles
    (Figure~\ref{fig:lpriver0}).
  %
    \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often but not
    exclusively linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles, and
    slow dip decay can also occur.
  %
    \item The rate of dip evolution can be used to place a model-dependent
    constraint on amount of material that is either being accreted or ejected
    during the state changes (Section~\ref{subsec:massflux}).
    Order of magnitude estimates require at least an asteroid belt's worth
    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or 100 times more 
    material if the occulting matter is gas.
  %
  \item The CQV phenomenon persists for $\gtrsim$150\,Myr, based on
    the existence of multiple CQVs in AB Dor, the Pleiades, and
    Psc-Eri (Section~\ref{subsec:starprops}).  It may even extend to
    200\,Myr, based on the one CQV we found in the Carina Near
    moving group (TIC~294328887; $\approx$200\,Myr).  The lack of
    detected CQVs in the Hyades and Praesepe suggests that the
    lifetime of the phenomenon is likely limited to the first few
    hundred million years.
	%
    \item The duty cycle for CQVs seems to be $\approx$$75$\%, based on
    the fraction of bonafide CQVs that turned on or turned off during
    TESS re-observations, two years after their initial observation.
  %
    \item While the majority of detected CQVs have masses of
    0.1-0.5\,$M_\odot$, the upper mass limit for the CQV phenomenon
    might extend into the K-dwarf regime ($<$$0.8$\,$M_\odot$).
    TIC~405754448 and TIC~405910546, with masses of $\approx$0.8 and
    $\approx$0.6 solar masses, are the two massive outliers
    (Section~\ref{subsec:extreme}), and we encourage additional
    scrutiny of these objects in future work.
  %
    \item The closest CQVs to the Sun are at distances of 15-20\,pc, and
    the brightest CQVs have $V$$\approx$12 ($J$$\approx$7.5).  This
    conclusion is an extrapolation from the CQV sample derived in this work
    being $\gtrsim$80\% complete within 20\,pc.  Expanding our analysis of
    the TESS data to the full frame images would yield a truly
    volume-limited selection function, and would expand the CQV census
    by about a factor of two within 50\,pc, and by a factor of ten
    within 100\,pc.
\end{enumerate}

@@

In both the gas and dust scenarios, CQVs are preferentially viewed
edge-on.
This implies that after correcting for the line-of-sight inclination,
at least one third of low mass stars
\citep{2022AJ....163..144G} trap circumstellar
material in the same way.
In addition, CQVs should preferentially show edge-on
transiting planets, at larger distances from the star than the
corotating material.
Given the interest level inherent to both of these points, important follow-up
observational work also includes searching for outer transiting
planets, and measuring equatorial velocities in
order to test whether the stellar inclination angles are indeed
preferentially edge-on.

>>>>

The most massive CQVs in our sample might represent an interesting new
regime.  To date, the only stars reported to show the CQV phenomenon
are M-dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
\citep{2022AJ....163..144G}.  TIC~405754448 and TIC~405910546 however
appear to have masses of $\approx$0.82 and $\approx$0.60\,$M_\odot$
respectively.  The next-highest masses are $\approx$0.40\,$M_\odot$.
The masses for the former two objects are consistent with their CAMD
locations, and their membership in LCC.  Based on its light curve
morphology, TIC~405910546 should be studied in greater depth, to
confirm it is not an eclipsing binary.  TIC~405754448 similarly shows
distinct morphology from many of the CQVs in Figure~\ref{fig:cqvs}, in
that it has some of the lowest amplitude dips.  While TIC~405754448
might be an unresolved binary (RUWE$_{\rm DR3}$=4.7),  the depth of
the coherent dips present in the Sector~11 light curve imply that the
CQV signal is indeed from the apparent primary of the system.  Taken
in sum, both of these objects seem to suggest that the CQV phenomenon
extends up in mass to pre-main-sequence K-dwarfs.

\subsection{TIC~425937691}

TIC~425937691 is a suprising case: it shows two seemingly independent
CQV signals on what appears to be the same star.  The two signals have
periods of $\approx$4.816\,hr and $\approx$3.218\,hr, respectively.
The former is the larger amplitude signal visible in
Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, corresponding to signal
with peak-to-peak amplitude of $\approx$8\%.  The latter signal is
only visible after subtracting the primary period, and it has a
sinusoidal envelope with a peak-to-peak amplitude of 2.5\%, and with
three sharp dips super-posed over each cycle.  The Gaia DR3 RUWE for
TIC~425937691 is 2.9.

The explanation that seems most likely for this source, given the two
photometric signals and the elevated RUWE, is an unresolved binary
consisting of two CQVs.  Recent work has shown that the orbits of
binaries closer than $\lesssim$700 AU tend to be aligned with their
planetary systems \citep{2022AJ....163..207C}.  If we assume that
observing CQV variability similarly requires near edge-on viewing
geometries, then we might expect a sufficiently close binary with one
CQV to also have another, since the spin axes in sufficiently close
binaries would tend to be aligned.  In this scenario, the two periods
being within $\approx$0.2\% of the 3:2 period commensurability would
simply be a coincidence.

@@

A clear link between the dense gas clumps (prominences) that likely
exist around rapidly rotating low-mass stars and the CQV phenomenon
has yet to be made.  A simple visual examination of the TESS light
curves for five prominence-hosting systems studied by
\citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and
V374 Peg--revealed no obvious CQV behavior, though all show
differential evolution, and Speedy~Mic shows two closely-spaced
periods and a strong beat.  Spectroscopically observable prominences
do not imply photometric CQV-like dips.

@@

\subsubsection{Gas absorption microphysics}
CQVs show broadband flux variations that can be 1-2$\times$ deeper in
the blue than in the red
\citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
For neutral hydrogen to produce this effect in absorption, its opacity
must be larger in the blue than in the red.
\citet{1992oasp.book.....G} suggests that this might be
microphysically possible: while bound-bound absorption provides
opacity only at narrow resonant lines, the hydrogen opacity due to
bound-free absorption is ``jagged'' \citep[see][Figure 8.5 and
Eq.~8.8]{1992oasp.book.....G}, such that at temperatures of
$\approx$3{,}000\,K to $\approx$10{,}000\,K the observed chromatic
transit depths might be reproduced.  Thompson scattering is ruled out
as a relevant opacity source, because it is gray.  The other plausible
alternative opacity source is dust, which also has a larger absorption
cross-section in the blue than the red \citep{1989ApJ...345..245C}.

An interesting point of comparison is the rapidly rotating magnetic
B-star, $\sigma$~Ori~E, which shows dips that are deeper in the blue
than in the red \citep{1977ApJ...216L..31H}.  Photometric and
spectroscopic observations of this star have been understood in terms
of absorbing circumstellar material, analogous to the geometries we
are discussing for much cooler M-dwarfs \citep{2005ApJ...630L..81T}.
This material however is unlikely to be dust, due to the relevant
sublimation timescales.  The opacity is instead thought to be sourced
from bound-free absorption from neutral hydrogen
\citep{2005ApJ...630L..81T}.  Separate and smaller-amplitude emission
in that system may also come from electrons scattering photospheric
light toward the observer when the clouds are not in transit
\citep{2022MNRAS.511.4815B}.

Given these complexities, it seems important for a future theoretical
study to be conducted to determine to what degree the observed
chromaticities in CQVs match, or do not match, expectations from
radiative transfer.  This issue has a key ability to resolve the
question of whether the CQVs are explained by dust or by gas, which
likely has bearing on whether the material producing the dips
is coming from the star, or whether it is a byproduct of the
protoplanetary disk.

@@

\subsubsection{The lifetime constraint}
Independent of the microphysical basis for gas absorption, the
observed lifetime of the CQV phenomenon could provide another
dimension to discern between the gas {\it vs.} dust clump scenarios.
Based on the available statistics from the studies by L.~Rebull and
J.~Stauffer, it seems plausible that CQV occurrence decreases in time,
bottoming to zero well before the $\approx$700\,Myr age of Praesepe.
This is odd in the context of the prominence scenario, because
pre-main-sequence M-dwarfs spin up over the first $\approx$$10^8$\,yr;
prominences might even be expected to be {\it more} common at the age
of the Pleiades than for younger stars.  This broadly assumes that any
star that can support prominences will, which translates in detail to
a condition on the star's mass, rotation period, and magnetic field
strength.  Based on the degree to which M-dwarfs remain rapid rotators
over the first 700\,Myr \citep[e.g. Figure~13
of][]{2022AJ....164...80R}, it seems surprising in the gas clump
(prominence) scenario that very few stars older than 150\,Myr have
been seen to exhibit the phenomenon.  In the dust clump scenario this
is not a problem, because if the dust were externally sourced, it
would be expected to have a finite supply.

@@

Planet occurrence rate studies from Kepler have shown that high-mass
M- dwarfs have $\approx$0.1 planets per star with sizes between
1-4\,$R_\oplus$ and orbital periods within 3 days
\citep{2015ApJ...807...45D}.  The number increases to $\approx$0.7
planets per star for planets with 1-4\,$R_\oplus$ and $P$$<$10\,days.
Extrapolating to all small close-in planets, with say
0.1-4\,$R_\oplus$ and within 10 days, it is reasonable to expect on
average one planet per M-dwarf.  TRAPPIST-1b ($P$=1.5\,days) is an
example of this type of planet, in orbit around a 0.08\,$M_\odot$ star
\citep{2017Natur.542..456G}.

In the context of planet formation, the stopping location for the
inner-most planet is set by the location of the protoplanetary disk's
truncation radius \citep{2018haex.bookE.142I}.  Although this disk
truncation radius is defined by equating the magnetic pressure from
the stellar magnetosphere with the ram pressure form the inflowing
gas, it also tends to roughly coincide with the Keplerian corotation
radius \citep{2016ARA&A..54..135H}.  Within models that have compact
multiplanet resonant chains migrate inward due to gas drag, the
inner-most planets arrive within $\approx$5-10 stellar radii before
the disk becomes depleted.

In this context, it is tempting to try to interpret features of the
CQV light curves in terms of the possible presence of close-in
exoplanets, or even planetesimals, that are expected to exist in
abundance around these stars.  Rocky planets this young could have
molten global magma oceans analogous to those that existed on the
Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus might be
undergoing significant outgassing and atmospheric escape.  However,
although it is {\it a priori} plausible that close-in rocky planets or
planetesimals could serve as a possible source of material for the
clouds, any evidence in support of such a picture currently seems
ambiguous at best.

@@

The planetesimal swarm model would predict that certain orbital phases
would produce recurrent dips if observed over sufficiently long
timescales, since the launching planetesimal would be massive enough
to remain in orbit, and similar to say K2-22 would stochastically
eject material.  While the regularity of the dip phases of LP~12-502
over the existing baseline (Figure~\ref{fig:lp2}) might agree with
this prediction, for most other CQVs (Figure~\ref{fig:evoln}) the data
seem to be in tension with this expectation.

There are a few additional problems for the idea of a disintegrating
planetesimal swarm.  First, many of the dips show asymmetries in the
wrong direction relative to the naive expectation of a trailing comet
tail.  Invoking non-exponentially decaying dust distributions as a
function of azimuth might be one way out of this, but such an idea
would need stronger theoretical footing.  Dynamical stability would be
a separate concern: in a model in which any new dip is ``explained''
by invoking a new planetesimal, one might eventually pack the
corotation radius to a degree where instability over short timescales
would be guaranteed.

@@

In identifying the two ambiguous CQVs with outlying SEDs (TICs~193136669 and
TIC~57830249; Section~\ref{subsec:irexcess}), we were prompted to reconsider our light curve-based
labeling, and ultimately concluded that these sources are dippers.  This
episode suggests that there could be overlap between CQVs and dippers.
It is also worth emphasizing that our labeling of e.g.~TIC~57830249
was based on a single sector of TESS data (Sector~36) when its
behavior is relatively periodic and it showed dip depths of a few
percent.  However in other TESS sectors (e.g. Sector~10), this source
looks completely different, varying in apparent flux by a factor of
two, with hardly any discernible periodicity at all.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{f8.pdf}
		\vspace{-0.1cm}
		\caption{
			{\bf The magnetic B-star connection}.
			HD~37776 (TIC~11400909) and HD~64740 (TIC~268971806) are
			magnetic B-stars with field geometries dominated by
			high order multipoles.
			Here, we compare their phased TESS light curves against the
			``best-matching'' CQV light curves, selected by eye from
			Figure~\ref{fig:cqvs}.
			Stellar masses approximate to one significant figure are given in the
			lower right of each panel; the star, TESS sector, and period are also noted.
		}
		\label{fig:bstar}
	\end{center}
\end{figure*}

@@

We can estimate the mass of a transiting cloud by first converting the
transit depth to an effective cloud radius, $R_{\rm cloud}$.  For most
CQVs in Figure~\ref{fig:cqvs}, this typically yields
$\approx$2-20\,$R_\oplus$.  This size can be converted into a mass
estimate by requiring the optical depth $\tau$ of the cloud to be at
least unity and by positing some composition for the cloud.  In other
words, a minimum constraint on the number density follows by requiring
the cloud to be optically thick.  For cases like LP 12-502, this is
reasonable because the transit duration implies $R_{\rm cloud}\ll
R_\star$.  Carrying out the relevant calculation assuming the
occulting material is dust grains 1\,$\mu$m in size,
\citet{2023MNRAS.518.4734S} find minimum cloud masses of order
$10^{12}$\,kg (their Eq.~23), which scale linearly with both the
optical depth and dust grain radius.  This is comparable to a small
asteroid; the asteroid belt itself has a mass of order
$\approx$10$^{21}$\,kg \citep{2019Icar..319..812P}.  The previously
discussed cool gas prominences would need to have masses of order
$10^{14}$\,kg \citep{1990MNRAS.247..415C}, about 100$\times$ larger
than the requisite dust mass.

@@

\subsection{Strengthening the magnetic B-Star connection}
Previous work by \citet{2017AJ....153..152S} noted an intriguing
connection between the CQVs and rapidly rotating magnetic B-stars such
as $\sigma$~Ori~E, which are known to have circumstellar gas clouds
trapped in corotation \citep{2005ApJ...630L..81T}.  Spectropolarimetry
has indicated that, similar to $\sigma$~Ori~E, most magnetic B-stars
have relatively simple field geometries that are predominantly
dipolar, though generally not aligned with the stellar spin axis
\citep{2009ARA&A..47..333D}.  Two exceptions to this rule are HD~37776
and HD~64740, which are B-stars that were previously known from
spectropolarimetry in the 2000s-2010s to have more complicated field
geometries - dominated by high order multipoles
\citep{2011ApJ...726...24K}.  It turns out, recent TESS light curves
of these two B-stars look surprisingly similar to the CQV light curves
\citep{2020pase.conf...46M}.  
Figure~\ref{fig:bstar} shows the phased TESS light curves for
the two outlying magnetic B-stars,
with by-eye ``best matching'' CQVs shown for comparison.
The number of dips per cycle, the shapes of the dips, and the dip
depths relative to the sinusoidal envelope, all seem to be quite
similar.
If this connection is taken seriously, then the implication would be
that the highly-structured M-dwarf light curves imply multipolar magnetic fields --
since that is the defining characteristic of these two B-stars,
relative to other known magnetic B stars like $\sigma$~Ori~E.

@@

\begin{enumerate}[leftmargin=*]
	%
	\item CQVs are quasiperiodic.  The mean periods remain fixed over the
		$>$1{,}000-cycle baseline of available observations; but the light curve shapes
		always evolve (Figure~\ref{fig:evoln}).
  %
  \item The same CQV can show dips with similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of its fundamental period,
    sometimes simultaneously, and each lasting for up to 50 cycles
    (Figure~\ref{fig:lpriver0}).
  %
    \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often but not
    exclusively linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles, and
    slow dip decay can also occur.
  %
    \item The rate of dip evolution can be used to place a model-dependent
    constraint on amount of material that is either being accreted or ejected
    during the state changes (Section~\ref{subsec:massflux}).
    Order of magnitude estimates require at least an asteroid belt's worth
    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or 100 times more 
    material if the occulting matter is gas.
  %
  \item The CQV phenomenon persists for $\gtrsim$150\,Myr, based on
    the existence of multiple CQVs in AB Dor, the Pleiades, and
    Psc-Eri (Section~\ref{subsec:starprops}).  It may even extend to
    200\,Myr, based on the one CQV we found in the Carina Near
    moving group (TIC~294328887; $\approx$200\,Myr).  The lack of
    detected CQVs in the Hyades and Praesepe suggests that the
    lifetime of the phenomenon is likely limited to the first few
    hundred million years.
	%
    \item The duty cycle for CQVs seems to be $\approx$$75$\%, based on
    the fraction of bonafide CQVs that turned on or turned off during
    TESS re-observations, two years after their initial observation.
  %
    \item While the majority of detected CQVs have masses of
    0.1-0.5\,$M_\odot$, the upper mass limit for the CQV phenomenon
    might extend into the K-dwarf regime ($<$$0.8$\,$M_\odot$).
    TIC~405754448 and TIC~405910546, with masses of $\approx$0.8 and
    $\approx$0.6 solar masses, are the two massive outliers
    (Section~\ref{subsec:extreme}), and we encourage additional
    scrutiny of these objects in future work.
  %
    \item Surprising analogs to the M- and K-dwarf CQVs exist in
    magnetic B-stars, but only those with multipolar field topologies.
    This suggests that the CQV dips and warps are strongly sculpted
    by the stellar magnetic fields, which would also be multipolar.
  %
    \item The closest CQVs to the Sun are at distances of 15-20\,pc, and
    the brightest CQVs have $V$$\approx$12 ($J$$\approx$7.5).  This
    conclusion is an extrapolation from the CQV sample derived in this work
    being $\gtrsim$80\% complete within 20\,pc.  Expanding our analysis of
    the TESS data to the full frame images would yield a truly
    volume-limited selection function, and would expand the CQV census
    by about a factor of two within 50\,pc, and by a factor of ten
    within 100\,pc.
\end{enumerate}

@@

In both the gas and dust scenarios, CQVs are preferentially viewed
edge-on.  This implies that after correcting for the line-of-sight
inclination, at least one third of low mass stars
\citep{2022AJ....163..144G} trap circumstellar material in the same
way.  This suggests that CQVs should preferentially show edge-on
transiting planets, at larger distances from the star than the
corotating material.  Given these points, important follow-up
observations should include searching for outer transiting planets,
and measuring equatorial velocities in order to test whether the
stellar inclination angles are indeed preferentially edge-on.
